---
title: "Ncollin 607 HW1"
output: pdf_document
author: "Noah Collin"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## R Markdown

Noah Collin

NOAH.COLLIN35@login.cuny.edu

This is Noah's HW1 for 607.  I'm using 538's Covid Polls data set available here: https://github.com/fivethirtyeight/covid-19-polls

The specific CSV I'm using describes the approval percentage of a President's performance in responding to Covid-19.


Below is a summary of the Polls CSV:
```{r}

#setwd("")
polls <- read.csv("covid_approval_polls.csv")
summary(polls)
```


Here are the top 5 rows of the uncleaned CSV:
```{r polls}

head(polls)
```
##Subset of Data
```{r polls2}
library(dplyr)
```
Here's just 4 columns of the data:

```{r pressure, echo=FALSE}
#plot(pressure)
temp <- select(
  .data = polls,
  end_date,
  approve,
  disapprove,
  subject
  )

head(temp)
#Filter to just have trump or Biden the subject.
temp <- filter(
  .data = temp,
  subject == "Trump" || subject == "Biden"
)


```

##Graph (I tried a few things that I couldn't get to work.  I'd hoped to turn in something better but ran out of time.)
```{r pollsGraph, ECHO = F}
ggplot(data = temp) + 
  geom_point(mapping = aes(x = end_date, y = approve)) 
#+ 
 # facet_grid(subject == "Trump" ~ subject == "Biden")

```
